NumPy---Array Programming in Python

### 2020-01-31 body.tex
Minor edits

Importantly, some projects follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but, often due to their development history, deviate in places.
Wherever there are such deviations, we often observe users gently requesting,
and developers evolving the software step by step towards the NumPy API,
provided this is possible and reasonable.

>>>>

Importantly, some projects follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but, often due to their development history, deviate in places.
Wherever there are such deviations, we often observe users gently requesting,
and developers evolving the software step by step toward the NumPy API.
